\huge A Usability Evaluation of Tor Launcher

### 2017-03-15 pets2017-paper/pets2017-paper.tex
Put references in Figure 1 and Figure 2 in order.

\section{Introduction}
Tor~\cite{dingledine2004tor} is an anonymity network that routes Internet traffic through a series of relays 
to make it difficult to observe sources and destinations. Tor Browser~\cite{torbrowser} is a modified Firefox browser that routes traffic through Tor, thereby simplifying the process of configuring Tor to use existing browsers. Although Tor Browser was originally designed for anonymity, many now use Tor Browser to circumvent Internet censorship. Many countries block Tor relays specifically to prevent their citizens from circumventing censorship~\cite{winter2012great}. Tor Browser is bundled with a graphical configuration interface, Tor Launcher (Figure~\ref{fig:old-interface}), which allows users to bypass censorship by configuring various bridges, proxies, and transport protocols prior to connecting to Tor. Of course, these configuration options are only effective if users understand how to correctly use them. Thus, we performed a usability study wherein we simulated various censorship environments in order to examine the effectiveness of Tor Launcher and how it could be improved.

@@

Technically, a proxy is any computer or service that allows its users to make indirect network connections to other services. In this sense, any Tor relay and the Tor circuit can also be considered to be a proxy. However, in this paper and more generally, the word ``proxy'' refers to a SOCKS or HTTP proxy that bypasses local firewalls. Figure~\ref{fig:topology} illustrates the potential network components involved in connecting to the Tor network.

@@

>>>>

\section{Introduction}
Tor~\cite{dingledine2004tor} is an anonymity network that routes Internet traffic through a series of relays 
to make it difficult to observe sources and destinations. Tor Browser~\cite{torbrowser} is a modified Firefox browser that routes traffic through Tor, thereby simplifying the process of configuring Tor to use existing browsers. Although Tor Browser was originally designed for anonymity, many now use Tor Browser to circumvent Internet censorship. Many countries block Tor relays specifically to prevent their citizens from circumventing censorship~\cite{winter2012great}. Tor Browser is bundled with a graphical configuration interface, Tor Launcher, which allows users to bypass censorship by configuring various bridges, proxies, and transport protocols prior to connecting to Tor. Of course, these configuration options are only effective if users understand how to correctly use them. Thus, we performed a usability study wherein we simulated various censorship environments in order to examine the effectiveness of Tor Launcher and how it could be improved.

@@

A connection to Tor involves many interacting components,
illustrated in Figure~\ref{fig:topology}.
It may involve a proxy and a bridge,
possibly in the presence of a censor.

Technically, a proxy is any computer or service that allows its users to make indirect network connections to other services. In this sense, any Tor relay and the Tor circuit can also be considered to be a proxy. However, in this paper and more generally, the word ``proxy'' refers to a SOCKS or HTTP proxy that bypasses local firewalls.

@@

Tor Launcher is the graphical user interface for configuring
an optional proxy, bridge, and transport
prior to initiating a connection to the Tor network.
Figure~\ref{fig:old-interface} shows the various screens
of Tor Launcher at the time we began our research.
